A Reduced Representation for Computational Fabrication

### 2013-05-03 thesis/abstract.tex
abstract future tense

\noindent Multi-material 3D printing allows objects to be composed of complex, heterogenous arrangements of materials. It is often more natural to define a functional goal than to define the material composition of an object. Translating these functional requirements to fabricable 3D prints is still an open research problem. Recently, several specific instances of this problem have been explored (e.g.,  appearance or elastic deformation), but they exist as isolated, monolithic algorithms. In this paper, we propose an abstraction mechanism that simplifies the design, development, implementation, and reuse of these algorithms. Our solution relies on two new data structures: a \emph{reducer tree} that efficiently parameterizes the space of material assignments and a \emph{tuner network} that describes the optimization process used to compute material arrangement. We provide an application programming interface for specifying the desired object and for defining parameters for the \emph{reducer tree} and \emph{tuner network}. We illustrate the utility of our framework by implementing several fabrication algorithms as well as demonstrating the manufactured results.

>>>>

\noindent Multi-material 3D printing allows objects to be composed of complex, heterogenous arrangements of materials. It is often more natural to define a functional goal than to define the material composition of an object. Translating these functional requirements to fabricable 3D prints is still an open research problem. Recently, several specific instances of this problem have been explored (e.g.,  appearance or elastic deformation), but they exist as isolated, monolithic algorithms. In this proposal, I propose an abstraction mechanism that simplifies the design, development, implementation, and reuse of these algorithms. The solution relies on two new data structures: a \emph{reducer tree} that efficiently parameterizes the space of material assignments and a \emph{tuner network} that describes the optimization process used to compute material arrangement. As part of thesis work, I will provide an application programming interface for specifying the desired object and for defining parameters for the \emph{reducer tree} and \emph{tuner network}. I will illustrate the utility of my new framework by implementing several fabrication algorithms as well as demonstrating the manufactured results.
